### 2021-11-23 input/proposal.tex
meow

@@

\begin{definition}[\label{def:lwo}Message staleness]
  Only the latest message of a \process matters. A message $m$ conveys
  \underline{s}tale control information if the \process that broadcast
  $m$ later broadcast another message $m'$: $\mathcal{S}(m)
  = \exists m': b_p(m) \rightarrow b_p(m')$.

  %% When a \process $p$ broadcasts two messages $b_p(m) \rightarrow
  %% b_p(m')$, no \process $q$ can deliver $m$ if it has delivered $m'$:
  %% $\nexists q \in V$ with $d_q(m') \rightarrow d_q(m)$, for $m$
  %% convey \emph{\underline{s}tale} control information: $S(m)$.
\end{definition}

Unfortunately, stale control information as stated in
Definition~\ref{def:lwo} may impair the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about deleted partitions.
\end{inparaenum}
Figure~\ref{fig:problem} depicts a scenario comprising only three
\processes $a$, $b$, $c$ chained with FIFO links, \ie where \processes
receive the messages in the order of their sending ($s_{pq}(m)
\rightarrow s_{pq}(m') \implies r_q(m) \rightarrow r_q(m')$). In
Figure~\ref{fig:problemA}, both $a$ and $c$ become sources, sending
their respective notification message to $b$. In
Figure~\ref{fig:problemB}, both $a$ and $c$ delete their partition
while $b$ receives, delivers, and forwards $\alpha_a^2$. In
Figure~\ref{fig:problemC}, $b$ receives, delivers, and forwards
$\alpha_c^1$, for it improves its best partition. Then it receives and
discards $\delta_a$, for its best partition does not match the deleted
one. It produces an echo but since $\alpha_c^3$ is already transiting
towards $a$, we simplify it. Finally, Figure~\ref{fig:problemD} shows
that eventually, $c$ stays in the deleted partition $P_a$ for not
having received $\delta_a$ that $b$ blocked earlier. As a cascading
effect, not only $c$ wrongfully believes that it belongs to $a$'s
partition when $a$ already deleted it, but it could contribute to its
inconsistency by blocking farther but up-to-date messages from actual
sources. The system needs to purge all stale messages to guarantee
consistent partitioning.

\begin{definition}[\label{def:purge}Message purge]
  A system \underline{p}urges a message $\TODO{\mathcal{P}}(m)$ when every
  \node $q$ that delivered $m$ eventually delivers another message
  $m'$ never followed by the delivery of the former message $m$:
  $d_q(m) \implies \exists m': \eventually (d_q(m)
  \rightarrow d_q(m') \wedge \neg (d_q(m') \rightarrow d_q(m)))$.
\end{definition}

@@

>>>>

\begin{definition}[\label{def:dcp}\underline{D}ynamic
  \underline{c}onsistent \underline{p}artitioning (DCP)]
  Dynamic consistent partitioning is consistent partitioning where
  \processes can join or leave the set of sources at any time.
\end{definition}

@@

\begin{definition}[\label{def:lwo}Stale messages]
  Only the latest message of a \process matters. A message $m$ conveys
  \underline{s}tale control information if the \process that broadcast
  $m$ later broadcast another message $m'$:
  $\mathcal{S}(m) = \exists m': b_x(m) \rightarrow b_x(m')$.
\end{definition}

Unfortunately, stale control information as stated in
Definition~\ref{def:lwo} may impair the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about deleted partitions.
\end{inparaenum}
Figure~\ref{fig:problem} depicts a scenario comprising only three
\processes $a$, $b$, $c$ chained with FIFO links, \ie where \processes
receive the messages in the order of their sending
($s_{pq}(m) \rightarrow s_{pq}(m') \implies r_q(m) \rightarrow
r_q(m')$). In Figure~\ref{fig:problemA}, both $a$ and $c$ become
sources, sending their respective notification message to $b$. In
Figure~\ref{fig:problemB}, both $a$ and $c$ delete their partition
while $b$ receives, delivers, and forwards $\alpha_a^2$. In
Figure~\ref{fig:problemC}, $b$ receives, delivers, and forwards
$\alpha_c^1$, for it improves its best partition. Then it receives and
discards $\delta_a$, for its best partition does not match the deleted
one. It produces an echo but since $\alpha_c^3$ is already transiting
towards $a$, we simplify it. Finally, Figure~\ref{fig:problemD} shows
that eventually, $c$ stays in the deleted partition $P_a$ for not
having received $\delta_a$ that $b$ blocked earlier. As a cascading
effect, not only $c$ wrongfully believes that it belongs to $a$'s
partition when $a$ already deleted it, but it could contribute to its
inconsistency by blocking farther but up-to-date messages from actual
sources. To reach consistent partitioning, \processes need
\begin{inparaenum}[(i)]
\item to purge all stale messages which
\item implies detecting possibly blocking conditions
\item by acknowledging the last partition of neighbors.
\end{inparaenum}

\begin{definition}[\label{def:purge}Message purge]
  A system \underline{p}urges a message when every \node $q$ that
  delivered $m$ eventually delivers another message $m'$ never
  followed by the delivery of the former message $m$:
  $d_q(m) \implies \exists m': \eventually (d_q(m) \rightarrow d_q(m')
  \wedge \neg (d_q(m') \rightarrow d_q(m)))$.
\end{definition}

\begin{lemma}[FB $\wedge$ \underline{F}orwarding of \underline{S}tale
  (FS) $\implies$ Detection]
  \TODO{meow!}
\end{lemma}

\TODO{rest to rework\ldots}

@@

\begin{definition}[\TODO{DCP $\implies$ eventual acknowledgement of at
    least one source}]
\end{definition}
